### 2023-08-28 appendix.tex
Acting on the comments on the appendix

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial vector $\textbf{u}$ and initial \alain{control-}state $q_0$.\alain{incohérent: control-state !, notation $q_0(\textbf{u})$  à utiliser}
To do so, we construct a reset-VASS $V_2$
with initial vector $\textbf{v}$ and initial state $q'_0$ \alain{idem}
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

@@

We add an additional transition $s$ \alain{s est d'habitude un état}
which reset the first two additional vector coordinate from control-state $q$.
% Transition $s$ is defined to have $r_1$ as an input and a null output.
This allows to disable the transitions of $V_1$ and to "freeze" the vector of $V_1$.
% This allows the token in $r_1$ to be removed, disabling all transitions in $T_1$ and "freezing" the marking of $P_1$.

@@

If we can always have some vector coordinate be not zero, then we can always fire some transition to add $+1$ to the penultimate additional coordinate.
% If we can always have some $p_i$ not be zero, then we can always fire some $s_{p_i}$, putting a token in $r_2$.
In this case we can add to the first additional coordinate again and assure that all transitions are live.
% In this case we must put a token back in $r_1$ and assure that all transitions in $C_2$ are live.
We must be sure that $V_2$ is live even if $V_1$ is {\em not} live.
% We must be sure that $C_2$ is live even if $C_1$ is {\em not} live.
% This is accomplished by a transition $s'$ which  "floods" the net $C_2$ with tokens, assuring that every transition is live if a token is ever put in $r_2$. Transition $s'$ has $r_2$ as its input and every place of $C_2$ as output
This is accomplished by a transition $s'$  \alain{s' est d'habitude un état}
which arbitrarily increments every other vector coordinate 
while decrementing the penultimate one and, additionally, a transition which 
substract from the last additional vector coordinate and add to the penultimate one.

>>>>

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial configuration $q_0(\textbf{u})$.
To do so, we construct a reset-VASS $V_2$
and an initial configuration $q'_0(\textbf{v})$ 
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

@@

We add an additional transition $t$ %\alain{s est d'habitude un état}
which reset the first two additional vector coordinate from control-state $q$.
% Transition $s$ is defined to have $r_1$ as an input and a null output.
This allows to disable the transitions of $V_1$ and to "freeze" the vector of $V_1$.
% This allows the token in $r_1$ to be removed, disabling all transitions in $T_1$ and "freezing" the marking of $P_1$.

@@

If we can always have some vector coordinate be not zero, then we can always fire some transition to add $+1$ to the penultimate additional coordinate.
% If we can always have some $p_i$ not be zero, then we can always fire some $s_{p_i}$, putting a token in $r_2$.
In this case we can add to the first additional coordinate again and assure that all transitions are live.
% In this case we must put a token back in $r_1$ and assure that all transitions in $C_2$ are live.
We must be sure that $V_2$ is live even if $V_1$ is {\em not} live.
% We must be sure that $C_2$ is live even if $C_1$ is {\em not} live.
% This is accomplished by a transition $s'$ which  "floods" the net $C_2$ with tokens, assuring that every transition is live if a token is ever put in $r_2$. Transition $s'$ has $r_2$ as its input and every place of $C_2$ as output
This is accomplished by a transition $t'$  %\alain{s' est d'habitude un état}
which arbitrarily increments every other vector coordinate 
while decrementing the penultimate one and, additionally, a transition which 
substract from the last additional vector coordinate and add to the penultimate one.
